Lapse & Vision Loss PS Analysis

### 2025-06-23 analysis.Rmd
update

      saveRDS(list(love_plot = love_plot, balance_plot = balance_plot, p_dist_plot = p_dist_plot, summary = balance_summary), file = diagnostics_filename)
    } else {
      print("Loading cached diagnostics...")
      diagnostics <- readRDS(diagnostics_filename)
      love_plot <- diagnostics$love_plot
      balance_plot <- diagnostics$balance_plot
      balance_summary <- diagnostics$summary
    }

>>>>

      saveRDS(list(love_plot = love_plot, balance_plot = balance_plot, p_dist_plot = p_dist_plot, summary = balance_summary), file = diagnostics_filename)
    } else {
      print("Loading cached diagnostics...")
      diagnostics <- readRDS(diagnostics_filename)
      love_plot <- diagnostics$love_plot
      balance_plot <- diagnostics$balance_plot
      p_dist_plot <- diagnostics$p_dist_plot
      balance_summary <- diagnostics$summary
    }
